Data Management for LSST Special Programs

### 2024-03-27 sec_intro.tex
fix typo

User-Generated Processing for Special Programs data will be necessary in cases that
do not meet the conditions of "possible and necessary" as defined in
Section~ref\{ssec:sci_sproc} and further illustrated in Section~\ref{ssec:proc_special}.
This will include cases where the science goals require custom algorithms or software,
or computational capacities which are beyond the Rubin-provided
computational resources (Section~\ref{ssec:sci_comp}).

>>>>

User-Generated Processing for Special Programs data will be necessary in cases that
do not meet the conditions of "possible and necessary" as defined in
Section~\ref{ssec:sci_sproc} and further illustrated in Section~\ref{ssec:proc_special}.
This will include cases where the science goals require custom algorithms or software,
or computational capacities which are beyond the Rubin-provided
computational resources (Section~\ref{ssec:sci_comp}).
